### 2015-07-01 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update report

\vspace*{2\baselineskip}
August 2014}}

@@

\section{Experimental Facility}
\label{sec:Experimental_Facility}

@@

\subsection{Fire Training Structure - Gas Cooling}
\label{sec:Burn_Building}

@@

\subsection{Concrete Structures - Fire Suppression}
\label{sec:Experimental Structures}

@@

The structures were instrumented for temperature, gas velocity, and heat flux measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~n) diameter inconnel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
% 	\caption{Instrumentation Legend}
% 	\label{fig:Instrumentation_Legend}
% \end{figure}

\subsection{Gas Cooling Instrumentation}
\label{subsec:Gas_Cooling_Instrumentation}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
	\caption{Photograph of the Instrumentation Dimensions in the Gas Cooling Experiments}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
\end{figure}

\subsection{Fire Suppression Instrumentation}
\label{subsec:Fire_Suppression_Instrumentation}

  A schematic plan view of the instrumentation arrangement is show in ????

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
	\caption{Photograph of the Instrumentation Dimensions in the Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Fog_Instrumentation}
	\caption{Photograph of the Instrumentation in the Fog Stream Tests.}
	\label{fig:Fog_Instrumentation}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Straight_Stream_Instrumentation}
	\caption{Photograph of the Instrumentation in the Straight Stream Tests.}
	\label{fig:Straigh_Stream_Instrumentation}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryInstrumentation}
	\caption{Photograph of the Instrumentation in the Fire Suppression Tests.}
	\label{fig:Fire_Suppression_Instrumentation}
\end{figure}

\subsection{Temperature}
\label{subsec:Temperature}

\subsubsection{Gas Cooling Experiments}
\label{subsubsec:Gas_Cooling_Temperature_Instrumentation}

\subsubsection{Fire Suppression Experiments}
\label{subsubsec:Fire_Suppression_Temperature_Instrumentation}

Thermocouple arrays were installed 2.0 m (6.7 ft) from both the east and the west walls of the burn room and 2.1 m (6.9 ft) from the south wall as shown in Figure ..  The vertical arrays had thermocouples located 0.03, 0.3, 0.61, 0.91, 1.22, 1.52, 1.83, 2.13 m below the bottom edge of the joist, where a ceiling would be installed.

In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.  In the hallway, there were seven thermocouples positioned vertically at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft)   In the south window opening, there were four thermocouples are located 0.28 m (0.95 ft), 0.58 (1.90 ft), 0.84 m (2.85 ft), and 1.16 m (3.8 ft) below the soffit.

\subsubsection{Gas Cooling Experiments}
\label{subsubsec:Gas_Cooling_Heat_Flux_Instrumentation}

\subsubsection{Fire Suppression Experiments}
\label{subsubsec:Fire_Suppression_Heat_Flux_Instrumentation}

In the northwest corner of the burn room two total heat flux gauges are located approximately 0.61 m (2 ft) out of the corner and 1.52 m (5 ft) below the ceiling, a position chosen to be representative of the height of a crawling firefighter's head.  One of the gauge's sensing surface is facing the ceiling and the other gauge is facing the pallets.  A similar heat flux gauge installation is located in the hallway, approximately 3.81 m (12.5 ft) from the burn room and 0.3 m (1ft) from the east wall of the hallway as shown in figure xx.  Again on gauge was facing the ceiling and one was facing the burn room.

\subsubsection{Gas Cooling Experiments}
\label{subsubsec:Gas_Cooling_Gas_Velocity_Instrumentation}

\subsubsection{Fire Suppression Experiments}
\label{subsubsec:Fire_Suppression_Gas_Velocity_Instrumentation}

\subsection{Mass}
\label{subsec:Mass}

\subsection{Moisture Content}
\label{subsec:Moisture_Content}

\subsection{Infrared Radiation}
\label{subsec:Infrared_Radiation}

@@

\section{Fuel Load: Gas Cooling}
\label{sec:Fuel_Load:_Gas_Cooling}

@@

\section{Fuel Load: Wood Experiments}
\label{sec:Fuel_Load:_Wood_Experiments}

@@

\section{Fuel Load: Furniture Experiments}
\label{sec:Fuel_Load:_Furniture_Experiments}

@@

\begin{sidewaystable}[!ht]
	\centering
	\caption{Fire Suppression Fuel masses}
	\renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{lllllll}
		\hline\noalign{\smallskip}
		Item               & Component		& Quantity		&  Material Description             							&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		2-seat New Sofa    &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
		           	 	   & \multirow{2}{*}{{Mattress}}	    & \multirow{2}{*}{{1 per sofa}}	& \multirow{2}{*}{\parbox{5cm} {Cover: 52~\% Polypropylene, 48~\% Polyester, Filling: 66~\% Polyester Fiber Pad, 34~\% Polyester Fiber  Batting}} & \multirow{2}{*}{{1.83 L X 1.21 W X 0.14 H}}  & \multirow{2}{*}{{14.6}}     \\
		           	 	   &	            &               &                                                          		&                            	&             		& \\[.25cm]
			           	   & Seat Cushion	& 2 per sofa	& 85~\% Urethane Foam, 15~\% Polyester Fiber   				    &  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
		Blue Chair         &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
		    			   & Seat Cushion   & 1 per chair   & 85~\% Urethane Foam, 15~\% Polyester Fiber					&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
		Blue/Green Chair   & 				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame     &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
		                   & Seat Cushion	& 1 per chair	& 85~\% Urethane Foam, 15~\% Polyester Fiber		            &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
		Paneling           &				& 8 panels		& 3.2 mm thick medium density fiberboard                   		&  2.44 L X 1.22 W X 3.2mm thick&  9    			& 72 \\
		Carpeting          &				& 22.26 m$^2$	& 100~\% PET Polyester                  						&  3.68 L X 6.05 W  			&  1.44 kg/m$^2$	& 32.2 \\
		Carpet Padding     &				& 22.26 m$^2$	& Polyurethane                 	 								&  3.68 L X 6.05 W X 11mm thick &  0.89 kg/m$^2$    & 19.8 \\
		                   &                &               &                                                               &                               & Total Mass        & 335.6 \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fire_Suppression_Fuel_Masses}
\end{sidewaystable}

@@

\chapter{References}
\label{chap:References}

>>>>

\vspace*{2\baselineskip}
August 2015}}

@@

\section{Experimental Facilities}
\label{sec:Experimental_Facility}

@@

\subsection{Fire Training Structure}
\label{sec:Burn_Building}

@@

\subsection{Concrete Block Structures}
\label{sec:Experimental Structures}

@@

The structures were instrumented for temperature, gas velocity, and heat flux measurements. Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples. Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements. The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter. The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconnel sheath. Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer). A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer. A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Pictures/Legend2}
	\caption{Instrumentation Legend.}
	\label{fig:Instrumentation_Legend}
\end{figure}

\subsection{Gas Cooling}
\label{subsec:Gas_Cooling_Instrumentation}

The gas cooling tests included 4 bare-bead thermocouple arrays  a bi-directional probe plus solid thermocouple array, and a total heat flux gauge/radiometer pair. Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the senors were located (cf. Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each of the bare-bead thermocouple array had 11 thermocouples. The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10ft) below the ceiling. There were 6 velocity probes and solid thermocouples centered at the external doorway to the gas cooling room. The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft), and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit. The total heat flux guage/radiometer were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
	\caption{Instrumentation Schematic for the Gas Cooling Experiments.}
	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
\end{figure}

\subsection{Fire Suppression}
\label{subsec:Fire_Suppression_Instrumentation}

The fire suppression testing included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux guage/radiometer pairs. Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (cf. Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each bare-bead thermocouple array had 8 thermocouples. The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling. The three bi-directional probe arrays had unique sensor locations. For the window array there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit. For the hallway array, the 7 sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling. The doorway array also had 7 sensor pairs, but the first sensors were located 0.15~m (0.5~ft) below the soffit. The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit. The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling. The pairs of total heat flux guages were set 1~m (3~ft) off the ground with one sense ``looking'' vertical and the other horizontal.

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
	\caption{Instrumentation Schematic for the Fire Suppression Experiments.}
	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
\end{figure}

% \subsection{Mass}
% \label{subsec:Mass}

% \subsection{Moisture Content}
% \label{subsec:Moisture_Content}

% \subsection{Infrared Radiation}
% \label{subsec:Infrared_Radiation}

@@

\section{Fuel Load}
\label{sec:fuel_load}

\subsection{Gas Cooling}
\label{sec:Fuel_Load_Gas_Cooling}

@@

\subsection{Fire Suppression}
\label{sec:Fuel_Load_Wood_Experiments}

@@

@@

\begin{sidewaystable}[!ht]
	\centering
	\scriptsize
	\caption{Fire Suppression Fuel masses}
	\renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{lllllll}
		\hline\noalign{\smallskip}
		Item               & Component		& Quantity		&  Material Description             							&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
		\noalign{\smallskip}\hline\noalign{\smallskip}
		2-seat New Sofa    &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
		           	 	   & \multirow{2}{*}{{Mattress}}	    & \multirow{2}{*}{{1 per sofa}}	& \multirow{2}{*}{\parbox{5cm} {Cover: 52~\% Polypropylene, 48~\% Polyester, Filling: 66~\% Polyester Fiber Pad, 34~\% Polyester Fiber  Batting}} & \multirow{2}{*}{{1.83 L X 1.21 W X 0.14 H}}  & \multirow{2}{*}{{14.6}}     \\
		           	 	   &	            &               &                                                          		&                            	&             		& \\[.25cm]
			           	   & Seat Cushion	& 2 per sofa	& 85~\% Urethane Foam, 15~\% Polyester Fiber   				    &  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
		Blue Chair         &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
		    			   & Seat Cushion   & 1 per chair   & 85~\% Urethane Foam, 15~\% Polyester Fiber					&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
		Blue/Green Chair   & 				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame     &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
		                   & Seat Cushion	& 1 per chair	& 85~\% Urethane Foam, 15~\% Polyester Fiber		            &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
		Paneling           &				& 8 panels		& 3.2 mm thick medium density fiberboard                   		&  2.44 L X 1.22 W X 3.2mm thick&  9    			& 72 \\
		Carpeting          &				& 22.26 m$^2$	& 100~\% PET Polyester                  						&  3.68 L X 6.05 W  			&  1.44 kg/m$^2$	& 32.2 \\
		Carpet Padding     &				& 22.26 m$^2$	& Polyurethane                 	 								&  3.68 L X 6.05 W X 11mm thick &  0.89 kg/m$^2$    & 19.8 \\
		                   &                &               &                                                               &                               & Total Mass        & 335.6 \\
		\noalign{\smallskip}\hline
	\end{tabular}
	\label{tab:Fire_Suppression_Fuel_Masses}
\end{sidewaystable}

@@
